---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# Discovering good data packages

## The state of data on CRAN

 * [List CRAN packages with data](R/get-pkgs-with-data-dir.R)

 * [Parsing DESCRIPTION files](R/parse_description.R)
 
 * [Parsing Rd files](R/get_metacran.R)
 
 * *Installing and loading packages*

## What makes a good data package?

https://docs.google.com/document/d/1xhJmt0v4p49jpwINNak9N7AMMb5yohTwwNOXH8WzqqQ/edit?usp=sharing

## Twitter Bot

https://twitter.com/rstatsdata

## Graphs

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8}
library(forcats)
library(tidyverse)
theme_set(theme_bw())

data_cran <- read_rds("data/description_metadata.rds") %>% 
  mutate(is_data_package = factor(is_data_package, levels=c("FALSE", "TRUE"), labels=c("Non-data packages", "Data packages")))

ggplot(data_cran, aes(is_data_package)) + 
  geom_bar() +
  labs(x=NULL)

ggplot(data_cran, aes(LazyData)) +
  geom_bar() +
  facet_wrap(~is_data_package)  + 
  theme(axis.text.x=element_text(angle = 90, hjust = 1))

ggplot(data_cran, aes(BugReports_is_not_na)) +
  geom_bar() +
  facet_wrap(~is_data_package) +
  labs(x = "Is there an BugReports in the package description?")

ggplot(data_cran, aes(URL_is_not_na)) +
  geom_bar() +
  facet_wrap(~is_data_package) +
  labs(x = "Is there an URL in the package description?")
```

```{r, echo=FALSE, fig.height=8}
# ggplot(data_cran, aes(License)) +
#   geom_bar() +
#   coord_flip() +
#   facet_wrap(~is_data_package)
```

```{r, echo=FALSE, fig.height=14}
df <- data_cran %>% 
  select(is_data_package, License) %>% 
  group_by(is_data_package, License) %>% 
  summarise(n=n())

df_wide <- df %>% 
  spread(is_data_package, n) %>% 
  mutate(`Non-data packages` = ifelse(is.na(`Non-data packages`), 0, `Non-data packages`),
         `Data packages` = ifelse(is.na(`Data packages`), 0, `Data packages`)) %>% 
  mutate(diff=`Data packages`-`Non-data packages`)

ggplot(df_wide, aes(fct_reorder(License, diff), diff)) +
  geom_col() + 
  coord_flip() +
  labs(x="License", y="<--- Non-data packages --------- Data packages --->") +
  theme(axis.text.y = element_text(size=8))
```

```{r fig.height=4, fig.width=6, echo=FALSE}
df_ts <- data_cran %>% 
  mutate(year = as.integer(strftime(data_cran$Published, format = "%Y"))) %>% 
  group_by(year, is_data_package) %>% 
  summarise(number = n())

ggplot(df_ts, aes(y = number, 
                      x = year, 
                      colour = is_data_package)) +
  geom_point() + 
  scale_y_log10()
```

## Flashboard

https://ropenscilabs.github.io/data-packages

## Potential Future Work

 * Scoring the quality of data in a package
 
 * Creating badges to advertise data quality

 * Use Github URLs to pull geo-location of package maintainers
 
 * Crawl Biocondunctor
 
 * Examine `inst/extdata` folders
